---
title: "Penguin Tabs"
author: "Jameel Alsalam"
date: "8/6/2021"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding=encoding, output_dir = "output", output_file = "penguin-tabs-interactive.html") })
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library("tidyverse")
library("palmerpenguins")

```

## R Markdown Tips

This R markdown document demonstrates a few techniques that I've been using lately:

  1) Putting alternate charts in HTML tabsets
  2) Generating the individual plots according to a template in a separate Rmd child/template document
  3) Keep my Rmd files in a /docs folder, but directing output to a /output folder
  4) Making sure the Rmarkdown can be worked with interactively or via targets and both work the same


```{r setupdata, include=FALSE}


```


A plot of all the data, drawn from the [example in palmerpenguins](https://allisonhorst.github.io/palmerpenguins/articles/examples.html):


```{r plotall}
flipper_bill <- penguins %>%
  filter(species == "Gentoo") %>%
  ggplot(aes(x = flipper_length_mm,
             y = bill_length_mm)) +
  geom_point(aes(color = species,
                 shape = species),
             size = 3,
             alpha = 0.8) +
  theme_minimal() +
  scale_color_manual(values = c(
                      "Adelie" = "darkorange", 
                      "Chinstrap" = "purple", 
                      "Gentoo" = "cyan4")) +
  scale_shape_manual(values = c(
                      "Adelie" = 16,
                      "Chinstrap" = 17,
                      "Gentoo" = 15)) +
  labs(title = "Flipper and bill length",
       subtitle = "Dimensions for Adelie, Chinstrap and Gentoo Penguins at Palmer Station LTER",
       x = "Flipper length (mm)",
       y = "Bill length (mm)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme(legend.position = c(0.85, 0.15),
        legend.background = element_rect(fill = "white", color = NA),
        plot.title.position = "plot",
        plot.caption = element_text(hjust = 0, face= "italic"),
        plot.caption.position = "plot")

flipper_bill
```


```{r plottext, results='asis'}
by_species_text <- map_chr(
  c("Adelie", "Chinstrap", "Gentoo"),
  ~knitr::knit_expand("docs/penguin-tabs-template.Rmd", pen_species = .x)
)

by_species_tabset_text <- c(
  "## By Species {.tabset}",
  by_species_text
) %>% paste0(collapse = '\n\n\n')
```

`r withr::with_dir("output", knitr::knit(text = by_species_tabset_text))`
